### 2018-04-05 Writing/draft.tex
Updated full manuscript

\subsection{Effect of character differences on topology}
As expected, there is a significant effect of the character difference in the ability to recover the correct topology.
The character difference metric can be seen as the inverse of character correlation (see Methods \ref{CD_description}): a high character difference approximates a low level of character correlation and vice versa.
When characters are correlated, one could expect the matrices to convey a really strong (but potentially misleading) phylogenetic signal since every character agrees with each other and conversely, when characters are uncorrelated, one could expect them to convey a weaker phylogenetic signal with a high amount of homoplasy.
Intuitively, this would lead the ``minimised'' character difference scenario to lead to incorrect but consistent trees, the ``maximised'' scenario to lead to poorly resolved once (really homoplasic trees) and the ``randomised'' scenario to perform the best at recovering the correct topology.
Although the expected results appear to be true for a low character difference scenario, increasing the character difference surprisingly improves the ability to recover the ``normal'' topology both in terms of clade conservation ($NTS_{RF}$) and taxa placement ($NTS_{Tr}$) for both inference methods (especially in bigger matrices; Figs \ref{Fig:RF_results_best} and \ref{Fig:Tr_results_best}).

% However, it is noteworthy to point that in rather small matrices, there was no significant difference in terms of recovering the right topology when maximising or randomising the character differences.
% Since many matrices are in this size range \citep{guillerme2016assessment} a simple bootstrap analysis (i.e. as an equivalent of randomising the character differences) can be sufficient to obtain good results (\textit{cf.} actively collecting different characters).
%MB: Agreed that that is noteworthy. I suspect I know why this happens (and you might have explained it earlier). It might actually be a statistical problem with our approach. When character similaritiy is maximized, how well resolved are the trees? 
%TG: I've moved that to a "potential application" paragraph in the discussion (please change the title of it, I had zero inspiration and find it ugly as feck!)

\subsubsection{Number of characters and taxa}
Because of the nature of our simulation protocol, one could expect that the effect of character correlation would have increased with the number of characters (i.e. the more characters available, the more characters are modified in each scenario).
Similarly, one could expect the number of taxa to have an effect of the raw ability to recover the ``normal'' topology (i.e. the more taxa, the more likely taxa are misplaced by chance.)

Although we measured a significant difference between ``small'' and larger matrices (both in terms of number of taxa and characters; Tables \ref{Tab_pooledscharacters_test} and \ref{Tab_pooledstaxa_test}), these differences have to be contrasted with the probability of overlap between the results distribution that is always really high between every matrices sizes (Bhattacharrya Coefficients $>0.965$ for both the different number of characters and taxa).
This suggest that the effect of character correlation on recovering the right topology is independent of the size of the matrix when pooling the data.
For the number of characters, this suggests that the overall character difference metric is a good proxy for character correlation and is independent of the number of characters analysed.
Similarly, using the a Normalised Tree Similarity metric ($NTS$) accounts for the fact that topological difference is affected by the sheer number of taxa considered (i.e. we corrected for the expected difference when comparing two random trees with the same number of taxa).

\subsection{Effect of character differences on the inference method}
When considering the pooled effect of the tree inference method, we only detected a significant difference between the Bayesian and the maximum parsimony trees in terms of clade conservation but none in terms of taxa placement (both using a Wilcoxon test and the Bhattacharrya Coefficient; Table \ref{Tab_pooledsmethods_test}).
The difference in the ability of each method to recover the ``correct'' topology has been heavily discussed in the last five years with some, indications that Bayesian inference will outperform parsimony when analysing discrete morphological characters alone (\citealt{wrightbayesian2014,OReilly20160081,puttick2017uncertain}; although some critics have raised issues with these investigations \citealt{spencerefficacy2013,goloboff2017weighted}).
In this study, it is possible that our simulation protocol for generating the characters (favouring slightly more M$k$-based characters rather than HKY ones) could slightly favour Bayesian inference over Parsimony, however, our protocol for selecting matrices \citep[i.e. those with in a $CI<0.26$ in a quick preliminary parsimony search;][]{OReilly20160081} could also favour Parsimony analysis.
It was however not the purpose of this study to compare the overall performance of both methods but rather to measure the effect of character correlation on each of those methods separately.

@@

\subsection{Distinction between different character correlations}
%TG: I've changed this paragraph - basically it's linking back to the intro saying the only correlation we should care about in phylogenetics is the one raising from data collection.
Here we mention three different types of character correlations but evolutionary biologists are mainly interested in the intra-organismal and evolutionary correlations (e.g. in evo-devo \citealt{goswami2006morphological}; or in macroevolution \citealt{fitzjohn2014much}).
These two types of correlations can only be studied \textit{a posteriori} with a phylogenetic hypothesis and should not used \textit{a priori} as a criterion to select characters.
In other words, intra-organisaml and evolutionary correlation should be studied based on an underlying phylogenetic framework making the correlation induced by data collection (i.e. coding correlation) the only type of correlation that can affect the phylogeny \textit{a priori}.
This dichotomy thus creates a trade of between: (1) coding fewer characters (stochastically reducing \textit{a priori} correlation) but making the \textit{a posteriori} correlation more dependent on the coding;
and (2) coding more characters (increasing \textit{a priori} dependence) but allowing the \textit{a posteriori} correlation being less dependent on the coding correlations.

@@

\subsection{Limitations}
%MB: I think what this section _really_ needs is an assessment of the method used to simulate correlations. It was basically accomplished by duplicating characters. It wasn't accomplished by evolving some characters with a particular covariance model (which probably would've been better). We kind of faked-up that model. 
%TG: agree.
First, simulating evolutionary history is complex.
Not only because the models we're using to infer phylogenies are ever improving \citep[e.g.][]{heath2014fossilized,Wright01072016} but also because generalising morphological evolution across vastly different organisms is probably impossible.
This can lead to spuriously generated discrete morphological matrices
However, we do not compare the ``maximised'', ``minimised'' and ``randomised'' to the ``true'' tree but rather to the ``normal'' tree.
This allows us to reduce the caveats from our simulations on the effect of character correlation since we only compare the simulation end products to each other (the outputs) rather than to the simulation inputs.

@@

However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise character correlation was not more significant than simply bootstrapping the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
For such matrices, minimising the character correlation (resampling characters $<25$\% different) or maximising it ($>75$\%) respectively significantly decreased and increased correct topological recovery compared to randomly resample matrices.
%TODO
%MB: But at what point? How much correlation is needed to affect it? TG: added values.

%MB: Part of it is: we expect it to be a problem, but _when_ do we expect it to be a problem. There's the issue of "check your data", but it only raises the question: how? I think this is where we suggest avenues for future research (either here or move it up to the discussion).

>>>>

\subsection{Effect of character differences on topology}
As expected, there is a significant effect of the character difference in the ability to recover the correct topology.
The character difference metric can be seen as the inverse of character correlation (see Methods \ref{CD_description}): a high character difference approximates a low level of character correlation and vice versa.
When characters are correlated, one could expect the matrices to convey a really strong (but potentially misleading) phylogenetic signal since every character agrees with each other and conversely, when characters are uncorrelated, one could expect them to convey a weaker phylogenetic signal with a high amount of homoplasy.
Intuitively, this would lead the ``minimised'' character difference scenario to lead to incorrect but consistent trees, the ``maximised'' scenario to lead to poorly resolved once (really homoplasic trees) and the ``randomised'' scenario to perform the best at recovering the correct topology.
Although the expected results appear to be true for a low character difference scenario, increasing the character difference surprisingly improves the ability to recover the ``normal'' topology both in terms of clade conservation ($NTS_{RF}$) and taxa placement ($NTS_{Tr}$) for both inference methods (especially in bigger matrices; Figs \ref{Fig:RF_results_best} and \ref{Fig:Tr_results_best}).
Furthermore, the trees generated by the ``minimised'' scenario do not appear better resolved (towards any topology) than the other scenarios (see Supplementary materials @@@).

\subsubsection{Number of characters and taxa}
Because of the nature of our simulation protocol, one could expect that the effect of character correlation would have increased with the number of characters (i.e. the more characters available, the more characters are modified in each scenario).
Similarly, one could expect the number of taxa to have an effect of the raw ability to recover the ``normal'' topology (i.e. the more taxa, the more likely taxa are misplaced by chance).

Although we measured a significant difference between ``small'' and larger matrices (both in terms of number of taxa and characters; Tables \ref{Tab_pooledscharacters_test} and \ref{Tab_pooledstaxa_test}), these differences have to be contrasted with the probability of overlap between the results distribution that is always really high between every matrices sizes (Bhattacharrya Coefficients $>0.965$ for both the different number of characters and taxa).
This suggest that the effect of character correlation on recovering the right topology is independent of the size of the matrix when pooling the data.
For the number of characters, this suggests that the overall character difference metric is a good proxy for character correlation as it is independent of the number of characters analysed.
Similarly, using the a Normalised Tree Similarity metric ($NTS$) accounts for the fact that topological difference is affected by the sheer number of taxa considered (i.e. we corrected for the expected difference when comparing two random trees with the same number of taxa).

\subsection{Effect of character differences on the inference method}
When considering the pooled effect of the tree inference method, we only detected a significant difference between the Bayesian and the maximum parsimony trees in terms of clade conservation but none in terms of taxa placement (both using a Wilcoxon test and the Bhattacharrya Coefficient; Table \ref{Tab_pooledsmethods_test}).
The difference in the ability of each method to recover the ``correct'' topology has been heavily discussed in the last five years with some indications that Bayesian inference will outperform parsimony when analysing discrete morphological characters alone (\citealt{wrightbayesian2014,OReilly20160081,puttick2017uncertain}; although some critics have raised issues with these investigations \citealt{spencerefficacy2013,goloboff2017weighted}).
In this study, it is possible that our simulation protocol for generating the characters (favouring slightly more M$k$-based characters rather than HKY ones) could slightly favour Bayesian inference over Parsimony, however, our protocol for selecting matrices \citep[i.e. those with in a $CI<0.26$ in a quick preliminary parsimony search;][]{OReilly20160081} could also favour Parsimony analysis.
It was however not the purpose of this study to compare the overall performance of both methods but rather to measure the effect of character correlation on each of those methods separately.

@@

\subsection{Distinction between different character correlations}
Here we mention three different types of character correlations but evolutionary biologists are mainly interested in the intra-organismal and evolutionary correlations (e.g. in evo-devo \citealt{goswami2006morphological}; or in macroevolution \citealt{fitzjohn2014much}).
These two types of correlations can only be studied \textit{a posteriori} with a phylogenetic hypothesis and should not used \textit{a priori} as a criterion to select characters.
In other words, intra-organisaml and evolutionary correlation should be studied based on an underlying phylogenetic framework making the correlation induced by data collection (i.e. coding correlation) the only type of correlation that can affect the phylogeny \textit{a priori}.
This dichotomy thus creates a trade of between: (1) coding fewer characters (stochastically reducing \textit{a priori} correlation) but making the \textit{a posteriori} correlation more dependent on the coding;
and (2) coding more characters (increasing \textit{a priori} dependence) but allowing the \textit{a posteriori} correlation being less dependent on the coding correlations.

@@

\subsection{Limitations}
First, simulating evolutionary history is complex.
Not only because the models we're using to infer phylogenies are ever improving \citep[e.g.][]{heath2014fossilized,Wright01072016} but also because generalising morphological evolution across vastly different organisms is probably impossible \citep[see constrasted discussions from][]{GoloboffEmpirical,OReillyEmpirical}.
However, we do not compare the ``maximised'', ``minimised'' and ``randomised'' to the ``true'' tree but rather to the ``normal'' tree.
This allows us to reduce the caveats from our simulations on the effect of character correlation since we only compare the simulation end products to each other (the outputs) rather than to the simulation inputs.

@@

However, in modest size matrices (25 taxa; 100 to 350 characters), the effect of actively choosing to minimise character correlation was not more significant than simply bootstrapping the matrix, suggesting that character correlation is more a problem in large discrete morphological matrices.
For such matrices, minimising the character correlation (resampling characters $<25$\% different) or maximising it ($>75$\%) respectively significantly decreased and increased correct topological recovery compared to randomly resample matrices.
